### 2017-12-28 Sections/essay_the_quantum_singularity.tex
Add X meas to cluster state ident, expanded multiplexers

\textit{--- Adiuva nos Deus.}

@@

Since there is positive computational leverage associated with quantum networking -- to all participating parties -- this creates a self-reinforcing economic quantum ecosystem, whereby all market participants are incentivised to continue contributing to the network, exponentially enhancing its collective power, with ever increasing returns over time. We will have reached a point of self-reinforcing exponential growth, driven by market forces. Because of the exponential scaling in computational power, it only becomes rational to ever-increasingly invest into further expansion, as every new qubit enhances the network more than the last.

@@

Since quantum algorithms provide quadratic speedup to \textbf{NP}-complete problems, and hence many optimisation problems, it follows that the existing distributed quantum computer will be able to perform self-enhancement by improving network routing efficiency, resource allocation, and even the design of the next generation of quantum computers, compared to what could be achieved using classical scheduling algorithms. This self-improvement will also be self-reinforcing -- as the quantum network becomes more powerful, its capacity for self-improvement will accelerate, at which point the self-enhancement becomes self-sustaining, without the need for human intervention or classical computers to guide the way.

@@

With the ability to perform accelerated machine learning, with post-classical capability, we will inevitably reach a point at which the quantum network becomes more intelligent than humans collectively. It will be able to invent, discover, prove, learn, and plan exponentially better than the human race who built it. At this point in time the entire economic framework for humanity will need to be reevaluated. How can there be economic demand for human labour when our technology makes both manual and intellectual human labour redundant? Conventional machines can already largely automate manual labour. If next the quantum network makes human intellect redundant, what will the place for the human race be in the world? Can a capitalist economic model survive the collapse in demand for human labour? How can money circulate in its absence? What paradigm will emerge in its place?

>>>>

\latinquote{Adiuva nos Deus.}

@@

Since there is positive computational leverage associated with quantum networking -- to \textit{all} participating parties, irrespective of size -- this creates a self-reinforcing economic quantum ecosystem, whereby all market participants are  increasingly incentivised to continue contributing to the network, exponentially enhancing its collective power, with ever increasing returns over time. We will have reached a point of self-reinforcing exponential growth, driven by market forces. Because of the exponential scaling in computational power, it only becomes rational to ever-increasingly invest into further expansion, as every new qubit enhances the network more than the last.

@@

Since quantum algorithms provide quadratic speedup to \textbf{NP}-complete problems, and hence many optimisation problems, it follows that the existing distributed quantum computer will be able to perform self-enhancement by improving network routing efficiency, resource allocation, and even the design of the next generation of quantum computers, compared to what could be achieved using classical scheduling and optimisation algorithms. This self-improvement will also be self-reinforcing -- as the quantum network becomes more powerful, its capacity for self-improvement will accelerate, at which point the self-enhancement becomes self-sustaining, without the need for human intervention or classical computers to guide the way.

@@

With the ability to perform accelerated machine learning, with post-classical capability, we will inevitably reach a point at which the quantum network becomes more intelligent than mankind collectively. It will be able to invent, discover, prove, learn, and plan exponentially better than the human race who built it. At this point in time the entire economic framework for humanity will need to be reevaluated.

How can there be economic demand for human labour when our technology makes both manual and intellectual human capital redundant? Conventional mechanical machines can already largely automate manual labour, making many occupations from our parents' generation obsolete. If next the quantum network makes human intellect redundant, what will the place for the human race be in the world? Can a capitalist economic model survive the collapse in demand for human labour? How can money circulate in its absence? What paradigm will emerge in its place?

### 2017-12-28 Sections/foreword.tex
Quantum simulation update
Latin quote stubs
Add X meas to cluster state ident, expanded multiplexers

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed'.\index{Zed}}, and classical networking \cite{bib:TanenbaumNet} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

@@

The theme music for this work may be found \href{http://soundcloud.com/peter-rohde/wir-sind-ein-volk}{here}\index{Theme music}.

\textit{--- Liber magnus est.}

>>>>

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed'.\cite{bib:NielsenChuang00}\index{Zed}}, and classical networking \cite{bib:TanenbaumNet} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

@@

The theme music for this work may be found \href{http://soundcloud.com/peter-rohde/wir-sind-ein-volk}{here} \copyright\index{Theme music}.

### 2017-12-28 Sections/models_for_quantum_computation.tex
Latin quote stubs
Add X meas to cluster state ident, expanded multiplexers

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{cluster_identities} \index{Cluster state identities}
	\caption{Several cluster state identities. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, while creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. \comment{Add X measurement identity}} \label{fig:cluster_ident} 
\end{figure}

>>>>

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{cluster_identities} \index{Cluster state identities}
	\caption{Several cluster state identities, demonstrated in the case of linear clusters. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, whilst creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. (d) Measurement of a qubit in the Pauli $\hat{X}$ basis removes that qubit, leaving one of its neighbours as a `dangling node'.} \label{fig:cluster_ident} 
\end{figure}

### 2017-12-28 Sections/optical_routers.tex
Latin quote stubs
Add X meas to cluster state ident, expanded multiplexers

@@

\subsection{Mechanical switches}

>>>>

The differing optical depths of linear and pyramid multiplexers lend themselves naturally to different applications. Suppose that in a network a single input-to-output route through a multiplexer is used far more often than the others. In that case, utilising a linear multiplexer will minimise average optical depth since that route can be designated to the first output port, which has an optical depth of only \mbox{$d=1$}. On the other hand, in a very balanced network, in which all optical routes are used roughly uniformly, the average case logarithmic optical depth of the pyramid multiplexer outperforms the average case linear optical depth of the linear multiplexer.

@@

\subsection{Mechanical switches}\index{Mechanical switches}
